---
title: "viz_part_1"
subtitle: "Part 1"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
```

##Load the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```
## Scatterplots

Create my first scatterplot 

```{r}
ggplot(weather_df,aes(x = tmin,y= tmax))+
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>% 
  ggplot(aes(x=tmin, y=tmax))+geom_point()
```
Save and edit a plot object.

```{r}
weather_plot=
  weather_df %>% 
  ggplot(aes(x=tmin, y=tmax))

weather_plot+geom_point()
```
## Advanced scatterplot...

Start with the same one and make it fancy

```{r}
weather_df %>% 
  ggplot(aes(x= tmin, y = tmax, color= name))+
  geom_point()+
  geom_smooth(se=FALSE)
```
What about `aes` placement..?

```{r}
weather_df %>% 
 ggplot(aes(x= tmin, y = tmax))+
  geom_point(aes(color=name))+
  geom_smooth()
```
Let's facet some things!

```{r}
weather_df %>% 
  ggplot(aes(x= tmin, y = tmax, color= name))+
  geom_point(alpha= .2)+
  geom_smooth(se=FALSE)+
  facet_grid(. ~ name)
```
Let's combine some elements and try a new plot.

```{r}

weather_df %>% 
  ggplot(aes(x=date, y=tmax, color=name))+
  geom_point(aes(size=prcp), alpha=0.5)+
  geom_smooth(se=FALSE)+
  facet_grid(. ~ name)
```
## Some small notes

How many geoms have to exist

```{r}
weather_df %>% 
  ggplot(aes(x=tmin, y=tmax, color=name))+
  geom_smooth(se=FALSE)
```
You can use a neat geom!

```{r}

weather_df %>% 
  ggplot(aes(x=tmin, y=tmax))+
  geom_density2d()+
  geom_point()
```
## Univariate plots

Histograms are really great.

```{r}
weather_df %>% 
  ggplot(aes(x=tmin))+
  geom_histogram()
```

Can we add color...

```{r}
weather_df %>% 
  ggplot(aes(x=tmin, fill= name))+
  geom_histogram()+
facet_grid(. ~ name)
```
Let's try a new geometry!

```{r}
weather_df %>% 
  ggplot(aes(x=tmin, fill=name))+
  geom_density(alpha=.3, adjust=.5)
```
What about boxplots??

```{r}
weather_df %>% 
  ggplot(aes(x=name,y = tmin))+
  geom_boxplot()
```

Trendy plots 

```{r}
weather_df %>% 
  ggplot(aes(x= name, y= tmin, fill=name))+
  geom_violin(alpha=0.4)+
  stat_summary(fun="median")
```
Ridge plots-- the most popular plot of 2017

```{r}
weather_df %>% 
ggplot (aes(x= tmin, y= name))+
  geom_density_ridges(alpha=.3)
```
## Save and Embed

Let's save a scatterplot

```{r}
weather_plot=
weather_df %>% 
  ggplot(aes(x=tmin, y = tmax, color=name))+
  geom_point(alpha=0.5)

ggsave("./results/weather_plot.pdf", weather_plot, width=8, height=5)
```

What about embedding...

```{r}
weather_plot
```
```{r, fig.width=12, fig.height-6}
weather_plot
```

Embed at different size

```{r, width=12, height=6}
weather_plot

```

